TKT_MetabPaper_Analyses

### 2024-05-08 Aleah_Thesis_Figures.Rmd
update

@@

set1="Male 9 Day"
set2="Female 9 Day"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=row.names(FDR[FDR$AvS9MT <.05,])
s2=row.names(FDR[FDR$AvS9FT <.05,])

main = "9 Day Thorax DEGs"

@@

@@

sigs = row.names(FDR)[FDR$AvS9FT < 0.05]
FC.data = setNames(FC$AvS9FT, row.names(FC))
FDR.data = setNames(FDR$AvS9FT, row.names(FDR))

@@

Female 9 Day Thorax Biological Process GO Terms
```{r, echo = F,  fig.width= 10}

@@

Female 9 Day Thorax Biological Process GO Terms
```{r  echo = F, fig.align='left'}

@@

Female 9 Day Thorax Cellular Component GO Terms
```{r, echo = F,  fig.width= 10}

@@

Female 9 Day Thorax Cellular Component GO Terms
```{r  echo = F, fig.align='left'}

@@

Female 9 Day Thorax Molecular Function GO Terms
```{r, echo = F,  fig.width= 10}

@@

Female 9 Day Thorax Molecular Function GO Terms
```{r  echo = F, fig.align='left'}

@@

Female 9 Day Thorax KEGG Pathways
```{r, echo = F,  fig.width= 10}

>>>>

names(total.DEGs) = c('FH3', 'FH9', 'FH40',
                      'FT3', 'FT9', 'FT40',
                      'FA3', 'FA9', 'FA40',
                      NA,
                      'MH3', 'MH9',
                      'MT3', 'MT9',
                      'MA3', 'MA9')

total.DEGs = total.DEGs[c('FH3', 'MH3','FH9', 'MH9','FH40',
                      NA,
                      'FT3', 'MT3', 'FT9', 'MT9', 'FT40',
                      NA,
                      'FA3', 'MA3', 'FA9', 'MA9', 'FA40')]

xlabel = names(total.DEGs)

bp.color = c(rep("steelblue", 5), NA, 
             rep("gold2", 5), NA,
             rep("brown3", 5))

barplot(height = total.DEGs,
        names.arg = xlabel,
        beside = T,
        density = c(1000,50,1000,50,1000,0,1000,50,1000,50,1000,0,1000,50,1000,50,1000),
        col = bp.color,
        las = 2,
        xlab = "Sample",
        ylab = "Total DEGs",
        main = "Total DEGs in A4V vs Silent",
        ylim = c(0, 4700))
##abline(v = 11.5, lty =2)
legend('topright',
       inset=c(-.35,0),
       bty = 'n',
       legend = c('Head', 'Thorax', 'Abdomen'), 
       fill = c('steelblue', 'gold2', 'brown3'),
       pt.cex = 1,
       cex = 1)

reorder = c(1,3,5,2,4,6,
            7,9,11,8,10,12,
            13,15,17,14,16)

barplot(height = total.DEGs[reorder],
        names.arg = xlabel[reorder],
        beside = T,
        density = c(1000,1000,1000, 75,75,0,
                    1000,1000,1000, 75,75,0,
                    1000,1000,1000, 75,75,0),
        col = bp.color,
        las = 2,
        xlab = "Sample",
        ylab = "Total DEGs",
        main = "Total DEGs in A4V vs Silent",
        ylim = c(0, 4700))
##abline(v = 11.5, lty =2)
legend('topright',
       inset=c(-.3,0),
       bty = 'n',
       legend = c('Head', 'Thorax', 'Abdomen'), 
       fill = c('steelblue', 'gold2', 'brown3'),
       pt.cex = 1,
       cex = 1)

@@

set1="Male 9 Day"
set2="Female 40 Day"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=row.names(FDR[FDR$AvS9MT <.05,])
s2=row.names(FDR[FDR$AvS40FT <.05,])

main = "DEGs from 9 Day Male Thorax and 40 Day Female Thorax"

@@

Male 9 Day Thorax Cellular Component GO Terms
```{r, echo = F,  fig.width= 10}

@@

sigs = row.names(FDR)[FDR$AvS40FT < 0.05]
FC.data = setNames(FC$AvS40FT, row.names(FC))
FDR.data = setNames(FDR$AvS40FT, row.names(FDR))

@@

Female 40 Day Thorax Biological Process GO Terms
```{r, echo = F,  fig.width= 10}

@@

Female 40 Day Thorax Biological Process GO Terms
```{r  echo = F, fig.align='left'}

@@

Female 40 Day Thorax Cellular Component GO Terms
```{r, echo = F,  fig.width= 10}

@@

Female 40 Day Thorax Cellular Component GO Terms
```{r  echo = F, fig.align='left'}

@@

Female 40 Day Thorax Molecular Function GO Terms
```{r, echo = F,  fig.width= 10}

@@

Female 40 Day Thorax Molecular Function GO Terms
```{r  echo = F, fig.align='left'}

@@

Female 40 Day Thorax KEGG Pathways
```{r, echo = F,  fig.width= 10}

### 2024-05-08 Anna qPCR data/AnnaThesisA4VRNAseqFigures.Rmd
update

---
title: "Glycolysis Network"
author: "John Santiago"
date: "2023-12-06"
output: 
  bookdown::pdf_document2:
    number_sections: false
---

```{r setup, include=FALSE}
##knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(dev='svg', fig.width=9, fig.height=12, out.width = "9in", out.height = "12in")
```

- #### Figure \@ref(fig:fig1): GR.FC vs WT.FC

- #### Figure \@ref(fig:fig2): GR.MC vs WT.MC

- #### Figure \@ref(fig:fig3): GR.FDf vs WT.FDf

- #### Figure \@ref(fig:fig4): GR.MDf vs WT.MDf

- #### Figure \@ref(fig:fig5): GR.FOE vs WT.FOE

- #### Figure \@ref(fig:fig6): GR.MOE vs WT.MOE

- #### Figure \@ref(fig:fig7): GRF: C vs Df

- #### Figure \@ref(fig:fig8): GRM: C vs Df

- #### Figure \@ref(fig:fig9): WTF: C vs Df

- #### Figure \@ref(fig:fig10): WTM: C vs Df

- #### Figure \@ref(fig:fig11): GRF: C vs OE

- #### Figure \@ref(fig:fig12): GRM: C vs OE

- #### Figure \@ref(fig:fig13): WTF: C vs OE

- #### Figure \@ref(fig:fig14): WTM: C vs OE

@@

```{r echo = F, include = F}
library(plotly)
library(org.Dm.eg.db)
library(ggpubr)
library(performance)
library(pathview)
library(visNetwork)
library(org.Dm.eg.db)

@@

@@

```{r include = F}

##genes in the kegg pathway and their enzyme IDs
glycolysis.genes = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisGenesKEGGinfo.csv')
##Edge data for genes connecting metabolites
glycolysis.edges = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisEnzymeEdgesKEGGinfo.csv')
##Metabolites in the KEGG pathway with their ID
glycolysis.metabs = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisMetaboliteKEGGinfo.csv')

node.data = node.info('/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/R Code/dme00010.xml')

glycolysis.network = function(comparison.T, comparison.M){

##extracting position data for nodes
node.info = data.frame(ID = unlist(node.data$kegg.names, use.names = F),
                       number = rep(names(node.data$kegg.names),
                                    lengths(node.data$kegg.names)),
                       x = 0,
                       y = 0,
                       color = 0,
                       names = "")
node.info$x = node.data$x[node.info$number]
node.info$y = node.data$y[node.info$number]

##make new columns for transcriptomic data
glycolysis.genes$FBgn = ""
glycolysis.genes$Symbol = ""
glycolysis.genes$FC = 0
glycolysis.genes$pval = 1

##Isolate gene ID info for goi
temp = GeneIDKey[GeneIDKey$CG %in% glycolysis.genes$CG,]
row.names(temp) = temp$CG

##fill in new columns with transcriptomic data
glycolysis.genes$FBgn = temp[glycolysis.genes$CG,'FBgn']
glycolysis.genes$Symbol = temp[glycolysis.genes$CG,'Symbol']
glycolysis.genes$FC = TKT.EdgeR.FC[glycolysis.genes$FBgn, comparison.T]
glycolysis.genes$FC = TKT.EdgeR[glycolysis.genes$FBgn, comparison.T]

##make new columns for metabolomic data
row.names(glycolysis.metabs) = glycolysis.metabs$KEGG.ID
glycolysis.metabs$metabolomicsID = ""
glycolysis.metabs$FC = 0
glycolysis.metabs$pval = 1

##retrieve name used in metabolomic data for metabolite IDs in path
##including IDs associated with multiple metabolomic names
i = 1
while(i<=nrow(glycolysis.metabs)){
  if(length(grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)) > 0){
    glycolysis.metabs$metabolomicsID[i]= names(KEGG.Key[grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)])
  }
  i = i +1
}

##retrieve metabolite fold change and pvalue data
glycolysis.metabs$FC = log2(comparison.M[glycolysis.metabs$metabolomicsID, "FC"])
glycolysis.metabs$pval = -log10(comparison.M[glycolysis.metabs$metabolomicsID, "p"])

##using the positions for nodes (metabolites) only
metab.info = node.info[node.info$ID %in% glycolysis.metabs$KEGG.ID,]

metab.info$FC = glycolysis.metabs[metab.info$ID, 'FC']
metab.info$pval = glycolysis.metabs[metab.info$ID, 'pval']
metab.info$names = glycolysis.metabs[metab.info$ID, 'Metabolite']
metab.info$color = glycolysis.metabs[metab.info$ID, 'FC']
metab.info$size = glycolysis.metabs[metab.info$ID, 'pval']

color.pallette = colorRampPalette(c('royalblue', 'grey', "firebrick"))(401)

metab.info$color[metab.info$color > 1] = 1
metab.info$color[metab.info$color < -1] = -1
metab.info$color = (metab.info$color * 200) +201
metab.info$color = color.pallette[metab.info$color]
metab.info$color[is.na(metab.info$color)] = 'dimgrey'

metab.info$size = 10 + 10*abs(metab.info$size)
metab.info$size[is.na(metab.info$size)] = 10

metab.info$title = paste0(glycolysis.metabs[metab.info$ID, "metabolomicsID"],
                          "<br>log2(FC): ", signif(metab.info$FC,3),
                          "<br>pval: ", signif(10^-metab.info$pval,3))

nodes = data.frame(id = paste0(metab.info$names),
                   color = metab.info$color,
                   size = metab.info$size,
                   x = 2*metab.info$x,
                   y = 2*metab.info$y,
                   physics = F,
                   group = "",
                   title = metab.info$title)

glycolysis.edges$FBgn = ''
temp.glycolysis.path = glycolysis.edges

i = 1
while(i<=nrow(glycolysis.edges)){
  enzymeID = paste0(glycolysis.edges$enzyme[i], "$")
  if(nrow(glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme),])>0){
    temp = glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme), "CG"]
    temp = row.names(GeneIDKey[GeneIDKey$CG %in% temp,])
    temp2 = glycolysis.edges[rep(i, length(temp)),]
    temp2$FBgn = temp
  }else{
    temp2 = glycolysis.edges[i,]
  }
  temp.glycolysis.path = rbind(temp.glycolysis.path,temp2)

  i = i +1
}

glycolysis.edges = temp.glycolysis.path[(nrow(glycolysis.edges)+1):nrow(temp.glycolysis.path),]

glycolysis.edges$size = log10(ccm[glycolysis.edges[,'FBgn'], comparison.T])
glycolysis.edges$size[glycolysis.edges$size <1] = 1
glycolysis.edges$size[is.na(glycolysis.edges$size)] = 1
glycolysis.edges$size = 2*glycolysis.edges$size

glycolysis.edges$color = TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T]
## max color intensity is at FC of 2
glycolysis.edges$color[glycolysis.edges$color>2] = 2
glycolysis.edges$color[glycolysis.edges$color<(-2)] = -2
glycolysis.edges$color = 201+(glycolysis.edges$color *100)
glycolysis.edges$color = color.pallette[glycolysis.edges$color]
glycolysis.edges$color[is.na(glycolysis.edges$color)] = 'dimgrey'

glycolysis.edges$title = paste0(GeneIDKey[glycolysis.edges$FBgn, "Symbol"],
                          "<br>log2(FC): ", signif(TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T],3),
                          "<br>FDR: ", signif(TKT.EdgeR[glycolysis.edges[,'FBgn'], comparison.T],3),
                          "<br>", comparison.means[[comparison.T]][1], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][1]],3),
                          "<br>", comparison.means[[comparison.T]][2], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][2]],3))

edges = data.frame(from = glycolysis.edges$from.name,
                   to = glycolysis.edges$to.name,
                   arrows = glycolysis.edges$arrow,
                   color = glycolysis.edges$color,
                   width = glycolysis.edges$size,
                   title = glycolysis.edges$title,
                   physics = T)

nodes = data.frame(id = paste0(nodes$id),
                   color = nodes$color,
                   size = nodes$size,
                   x = nodes$x,
                   y = nodes$y,
                   physics = F,
                   group = "",
                   title = nodes$title)

OutsidePath = data.frame(id = c('Pentose Phosphate Pathway',
                               'Propanoate Metabolism',
                               'Starch and Sucrose Metabolism',
                               'Citrate Cycle'),
                        color = "black",
                        size = 15,
                        x= c(1350,1254,966,175),
                        y=c(1112,1822,110,1700),
                        physics = F,
                        group = 'Outside Path',
                        title = "")

nodes = rbind(nodes, OutsidePath)

visNetwork(nodes, edges, main = paste0(comparison.means[[comparison.T]][1], " vs ", comparison.means[[comparison.T]][2]))%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows = edges$arrows)%>%
  visGroups(groupname = "Outside Path", shape = 'box', physics=F, size = 25, font=list(color="white"))

}

@@

```{r echo = F, fig.height=12, fig.width=9, fig.align='left', fig1, fig.cap = 'G85R relative to WT. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRxWT.FC', comparison.M = GRxWT.C)

@@

```{r, echo =F, fig2, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R relative to WT. Transcriptomic data is from males and metabolomic data is from both sexes.Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRxWT.MC', comparison.M = GR.CxDf)

@@

```{r, echo =F, fig3, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R TKT-Df relative to WT TKT-Df. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRxWT.FDf', comparison.M = GRxWT.Df)

@@

```{r, echo =F, fig4, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R TKT-Df relative to WT TKT-Df. Transcriptomic data is from males and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRxWT.MDf', comparison.M = GRxWT.Df)

@@

```{r, echo =F, fig5, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R TKT-OE relative to WT TKT-OE. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRxWT.FOE', comparison.M = GRxWT.OE)

@@

```{r, echo =F, fig6, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R TKT-OE relative to WT TKT-OE. Transcriptomic data is from males and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRxWT.MOE', comparison.M = GRxWT.OE)

```{r, echo =F, fig7, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R control relative to G85R TKT-Df. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRF.CxDf', comparison.M = GR.CxDf)

```{r, echo =F, fig8, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R control relative to G85R TKT-Df. Transcriptomic data is from males and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRM.CxDf', comparison.M = GR.CxDf)

```{r, echo =F, fig9, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'WT control relative to WT TKT-Df. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'WTF.CxDf', comparison.M = WT.CxDf)

```{r, echo =F, fig10, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'WT control relative to WT TKT-Df. Transcriptomic data is from males and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'WTM.CxDf', comparison.M = WT.CxDf)

```{r, echo =F, fig11, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R control relative to G85R TKT-OE. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRF.CxOE', comparison.M = GR.CxOE)

```{r, echo =F, fig12, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R control relative to G85R TKT-OE. Transcriptomic data is from males and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRM.CxOE', comparison.M = GR.CxOE)

```{r, echo =F, fig13, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'WT control relative to WT TKT-OE. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'WTF.CxOE', comparison.M = WT.CxOE)

```{r, echo =F, fig14, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'WT control relative to WT TKT-OE. Transcriptomic data is from males and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'WTM.CxOE', comparison.M = WT.CxOE)

>>>>

---
title: "Anna Thesis A4V RNAseq KEGG Pathway Figures"
author: "John Santiago"
date: "2024-03-27"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r echo = F, include = F}
library(plotly)
library(org.Dm.eg.db)
library(pathview)
library(visNetwork)
library(org.Dm.eg.db)

@@

metab.id = setNames(row.names(GRxWT.C), GRxWT.C$KEGG)
mixed.id = unlist(strsplit(names(metab.id)[grep(" / ", names(metab.id))], " / "))
mixed.id = mixed.id[mixed.id != "n/a"]
mixed.id = setNames(rep("", length(mixed.id)), mixed.id)

i = 1
while(i<=length(mixed.id)){
  mixed.id[i] = metab.id[grep(names(mixed.id)[i], names(metab.id))]
  i = i +1
}

metab.id = metab.id[-grep(" / ", names(metab.id))]

metab.id = c(metab.id, mixed.id)

@@

```{r echo = F}
KEGG.diagram = function(PathwayID, out.id, FC.data, FDR.data){
  ##KEGG Mapping Function
  if(length(intersect(list.files(), "KEGG_Image_Files")) == 0){
    dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
    }
  Home = dirname(rstudioapi::getSourceEditorContext()$path)
  OutputDir = paste0(Home, "/KEGG_Image_Files/")
  setwd(OutputDir)
  sigs = names(FDR.data)
  ##sigs = names(FDR.data[FDR.data <= .05])

  if(class(FC.data)=="numeric"){
    deg.data=setNames(FC.data[sigs],GeneIDKey[sigs, "ensembl"])
  }

  if(class(FC.data)=="data.frame"){
    deg.data = as.matrix(FC.data)
    row.names(deg.data) = GeneIDKey[row.names(FC.data), "ensembl"]
  }

  metab.data = setNames(log2(metab.data[metab.id, 'FC']), names(metab.id))

  pv.out <- pathview(gene.data =  deg.data,
                     ##cpd.data = metab.data,
                   pathway.id = PathwayID,
                   species = "dme",
                   kegg.native = T,
                   limit=list(gene=c(-2,2)),
                   node.sum="max.abs",
                   low="royalblue",mid = "grey",high="firebrick",
                   out.suffix = out.id,
                   bins=list(genes=30),
                   plot.col.key = F,
                   match.data = F)
  setwd(Home)

    if(class(FC.data)=="numeric"){
      img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".png")
    }

    if(class(FC.data)=="data.frame"){
      img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".multi.png")
    }
  knitr::include_graphics(img.file)
}

@@

```{r echo = F, message=F, fig.width=7}

PathwayID = "00010"
out.id = 'G85R_F'
FC.data = setNames(TKT.EdgeR.FC$GRxWT.FC, row.names(TKT.EdgeR.FC))
FDR.data = setNames(TKT.EdgeR$GRxWT.FC, row.names(TKT.EdgeR))

FC.data = TKT.EdgeR.FC[,c('GRxWT.FC', 'GRxWT.MC')]
FDR.data = setNames(TKT.EdgeR$GRxWT.MC, row.names(TKT.EdgeR))

metab.data = GRxWT.C
KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)

@@

```{r echo = F, message=F, fig.width=7}

PathwayID = "00020"
out.id = 'G85R_F'
FC.data = setNames(TKT.EdgeR.FC$GRxWT.FC, row.names(TKT.EdgeR.FC))
FDR.data = setNames(TKT.EdgeR$GRxWT.FC, row.names(TKT.EdgeR))

FC.data = TKT.EdgeR.FC[,c('GRxWT.FC', 'GRxWT.MC')]
FDR.data = setNames(TKT.EdgeR$GRxWT.MC, row.names(TKT.EdgeR))

metab.data = GRxWT.C
KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)

@@

```{r echo = F, message=F, fig.width=7}

PathwayID = "00061"
out.id = 'G85R_F'
FC.data = setNames(TKT.EdgeR.FC$GRxWT.FC, row.names(TKT.EdgeR.FC))
FDR.data = setNames(TKT.EdgeR$GRxWT.FC, row.names(TKT.EdgeR))

FC.data = TKT.EdgeR.FC[,c('GRxWT.FC', 'GRxWT.MC')]
FDR.data = setNames(TKT.EdgeR$GRxWT.MC, row.names(TKT.EdgeR))

metab.data = GRxWT.C
KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)

@@

```{r echo = F, message=F, fig.width=7}

PathwayID = "04214"
out.id = 'G85R_F'
FC.data = setNames(TKT.EdgeR.FC$GRxWT.FC, row.names(TKT.EdgeR.FC))
FDR.data = setNames(TKT.EdgeR$GRxWT.FC, row.names(TKT.EdgeR))

FC.data = TKT.EdgeR.FC[,c('GRxWT.FC', 'GRxWT.MC')]
FDR.data = setNames(TKT.EdgeR$GRxWT.MC, row.names(TKT.EdgeR))

metab.data = GRxWT.C
KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)

@@

```{r echo = F, message=F}

PathwayID = "04137"
out.id = 'G85R_F'
FC.data = setNames(TKT.EdgeR.FC$GRxWT.FC, row.names(TKT.EdgeR.FC))
FDR.data = setNames(TKT.EdgeR$GRxWT.FC, row.names(TKT.EdgeR))

FC.data = TKT.EdgeR.FC[,c('GRxWT.FC', 'GRxWT.MC')]
FDR.data = setNames(TKT.EdgeR$GRxWT.MC, row.names(TKT.EdgeR))

metab.data = GRxWT.C
KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)

@@

### 2024-05-08 TKT_RNAseq/R Code/GlycolysisNetwork.Rmd
update

```{r echo = F, include = F}
library(plotly)
library(org.Dm.eg.db)
library(ggpubr)
library(performance)
library(pathview)
library(visNetwork)
library(org.Dm.eg.db)

@@

glycolysis.network(comparison.T = 'GRxWT.MC', comparison.M = GR.CxDf)

>>>>

```{r echo = F, include = F}
library(plotly)
library(org.Dm.eg.db)
##library(ggpubr)
##library(performance)
library(pathview)
library(visNetwork)
library(org.Dm.eg.db)

@@

glycolysis.network(comparison.T = 'GRxWT.MC', comparison.M = GRxWT.C)

### 2024-05-08 TKT_RNAseq/R Code/PurineMetabolismNetwork.Rmd
update

---
title: "TKT_MetabPaper_Analyses"
author: "John Santiago"
date: "2023-09-29"
output: 
  bookdown::html_document2:
    number_sections: false
---

@@

```{r echo = F, include = F}
library(plotly)
library(org.Dm.eg.db)
library(ggpubr)
library(performance)

>>>>

---
title: "TKT_MetabPaper_Analyses"
author: "John Santiago"
date: "2023-09-29"
output: html_document
---

@@

```{r echo = F, include = F}
library(plotly)
library(org.Dm.eg.db)
##library(ggpubr)
##library(performance)
